%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

% TODO: Figure out how to make this less of a mess. 
%---------------------------------------------------------
  \cventry
    {} % Role
    {bDocs} % Event
    {} % Location
    {} % Date(s)
    {
      \vspace{-9mm}
      \begin{cvprojectitems}
        \item A single-page web application for collaborative, real-time, in-browser rich text and code editing.
        \item Supports synchronized text editing across multiple users, along with importing text documents, synchronized settings 
        (language, font size) and titles, and displaying recently accessed documents.
        \item Built using \textbf{React} and \textbf{Semantic UI}. Backed by a \textbf{Firebase} Realtime Database. 
      \end{cvprojectitems}
    }

%---------------------------------------------------------
  \vspace{-3mm}
  \cventry
    {} % Role
    {PaperJS Parsons} % Event
    {} % Location
    {} % Date(s)
    {
      \begin{cvprojectitems}
        \vspace{-9mm}
        \item A web application used as an interface to solve practice Parsons Problems. Used to help teach students 
        Paper.js, a graphics scripting library.
        \item Allows users to run and see the effects of their code, and displays interactive examples 
        for users to compare the results of their submissions with.
        \item Developed collaboratively as part of a preliminary stage of research into the efficacy of Parsons Problems, 
        a new type of practice problem introduced to improve computer science education.
        \item Written in \textbf{HTML} and \textbf{JavaScript}, using the Bootstrap, jQuery, and Paper.js libraries.
      \end{cvprojectitems}
    }
\end{cventries}
